Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2024-04-18 revision-1/lang.tex
checkpoint

@@

\emph{Memories} are fundamental to the semantics of $\fedcat$ and
provide the random tape and secret inputs to protocols, and record
view assignments. Memories $\store$ are finite (partial) mapping from
variables to values $v \in \mathbb{Z}_p$. The \emph{domain} of a
memory is written $\dom(\store)$ and is the finite set of variables on
which the memory is defined. We write $\store\{ x \mapsto v\}$ for
$x\not\in\dom(\store)$ to denote the memory $\store'$ such that
$\store'(x) = v$ and otherwise $\store'(y) = \store(y)$ for all $y
\in \dom(\store)$. We write $\store_1 \subseteq \store_2$ iff
$\dom(\store_1) \subseteq \dom(\store_2)$ and $\store_1(x) =
\store_2(x)$ for all $x \in \dom(\store_1)$. We write $\store_1 \cap
\store_2$ to denote the combination of $\store_1$ and $\store_2$
assuming $\store_1(x) = \store_2(x)$ for all $x \in \dom(\store_1)
\cap \dom(\store_2)$, otherwise $\store_1 \cap \store_2$ is undefined.
We write $\store_1 \subseteq \store_2$ iff $\store_1 \cap \store_2
= \store_1$.

>>>>

\subsubsection{Library Functions}

@@

\emph{Memories} are fundamental to the semantics of $\fedcat$ and
provide random tape and secret inputs to protocols, and also record
message sends, public broadcast, and client outputs. Memories $\store$ are finite
(partial) mapping from variables $x$ to values $v \in \mathbb{Z}_p$. The \emph{domain} of a
memory is written $\dom(\store)$ and is the finite set of variables on
which the memory is defined. We write $\store\{ x \mapsto v\}$ for
$x\not\in\dom(\store)$ to denote the memory $\store'$ such that
$\store'(x) = v$ and otherwise $\store'(y) = \store(y)$ for all $y
\in \dom(\store)$. We write $\store_1 \subseteq \store_2$ iff
$\dom(\store_1) \subseteq \dom(\store_2)$ and $\store_1(x) =
\store_2(x)$ for all $x \in \dom(\store_1)$. We write $\store_1 \cap
\store_2$ to denote the combination of $\store_1$ and $\store_2$
assuming $\store_1(x) = \store_2(x)$ for all $x \in \dom(\store_1)
\cap \dom(\store_2)$, otherwise $\store_1 \cap \store_2$ is undefined.
We write $\store_1 \subseteq \store_2$ iff $\store_1 \cap \store_2
= \store_1$.
